Community-Conditioned Language Models

### 2021-05-18 paper/paper.tex

\begin{figure}
  \includegraphics[width=\linewidth]{floats/confusion_lstm-3-1}
\caption{
  Log-probability LMCC confusion matrix for the LSTM model with $l_c=1$. 
  Communities are sorted by indiscernability. (The first communities predominantly use a language other than English, and are thus very discernable.)}
\label{fig:confusion}
\end{figure}

@@

The \(d(L,S)\) metric ranges from \(0\) (corresponding to perfect
independence) to \(n\) (corresponding to perfect correlation, obtained
for example if \(L=S\)), where $n=510$ is the number of communities
considered.

To get a more precise sense of what value of \(d(L,S)\) indicates significant correlation,
We have computed experimentally \(d(L,S)\) for 
\(L\) and \(S\) chosen as random 16 dimensions. We find
a mean \(μ_d\)=TODO and a standard deviation \(σ_d\)=TODO.\jp{Unfortunate overloading}

TODO: !!! we should take the correlation of a random 16 × 510 with the web embeddings !!!

Thus if \(d(L,S)\) is below \(μ_d-3σ_d\), we can safely assume that there % below, because we have a distance rather than correlation in this convention.
is statistically significant correlation between \(L\) and
\(S\). However, below, we will also give a sense of \emph{how} the
correlation is manifested by analysis of the two principal components
of correlation in the linguistic embeddings, \(U_0\) and \(U_1\). To
do so we will plot the projection of embeddings on along \(U_0\) and
\(U_1\), together with the corresponding singular values.

>>>>

\begin{figure}
  \includegraphics[width=\linewidth]{floats/confusion_lstm-3-1}
\caption{
  LMCC confusion matrix for the LSTM model with $l_c=1$, showing $\log(P(c_j\mid c_i))$, 
  with $c_i$ on the x-axis and $c_j$ on the y-axis.
  Communities are sorted by indiscernability.
  (The first few communities predominantly use a language other than English, and are thus very discernable.)}
\label{fig:confusion}
\end{figure}

@@

The \(d(L,S)\) metric ranges from \(0\) 
(corresponding to perfect correlation, 
obtained for example if \(L=S\)) 
to \(n\) 
(corresponding to perfect independence), 
where $n=510$ is the number of communities considered.

To get a more precise sense of what value of \(d(L,S)\) indicates significant correlation,
We have experimentally computed \(d(L,S)\) for five random  ``embeddings'' 
with the same shape as the CCLM embeddings.
We observed a mean of \(μ_d=431.39\) and a (Bessel's-corrected) 
standard deviation \(s_d=3.94\) in their distance from the social embedding, \(S\). %\jp{Unfortunate overloading} luckily it seems that sample stdev is often written with an $s$ to differentiate from population stdev

Thus if \(d(L,S)\) is below \(419.56\)
($\mu_d - 3s_d$), 
we can safely assume that there 
is statistically significant correlation between \(L\) and
\(S\). 
Indeed, this is very clearly the case (\cref{tab:embedding-correlations}),
meaning that the CCLM embedding capture some of the same information as the
social-network embeddings.
We also give a sense of \emph{how} the
correlation is manifested by analysis of the two principal components
of correlation in the linguistic embeddings, \(U_0\) and \(U_1\). To
do so we plot the projection of embeddings on along \(U_0\) and
\(U_1\), together with the corresponding singular values.

\begin{table}
\centering
\begin{tabular}{llcc}
\toprule
                        &   & LSTM     & Transformer \\
\midrule
  \multirow{4}{*}{$l_c$}  & 0 &         254.06  (44.99) &         239.41  (49.09)  \\
                          & 1 &         245.14  (47.25) & \textbf{232.18} (50.38)   \\
                          & 2 &         249.17  (46.23) &         233.47  (50.21)  \\
                          & 3 & \textbf{241.13} (48.27) &         237.74   (49.13) \\
\bottomrule
\end{tabular}
\caption{Distance between CCLM embeddings and the social network-based embedding
of \citet{Kumar2018}, as measured by $d(L,S)$. In parentheses is the number of standard deviations
from the mean distance of our random embedding sample.} \label{tab:embedding-correlations}
\end{table}
